No Replication Without Process Documentation:  An Assessment of Management

### 2019-10-03 MSE manuscript.Rmd
Edit results section

# Get map background for plotting the map
world <- borders("world", colour="gray50", fill="gray50", alpha=0.75) # create a layer of borders

# Where MSEs have occured
map.data<-rbind(data_pub,data_CC) %>%
  select(map.col) %>%
  mutate(Drivers=str_extract(Drivers, "Climate Change")) %>%
  mutate(Drivers=replace_na(Drivers, "Random Sample"))

@@

Driver.plot<-ggplot(drive.data,aes(x=order,y=Percent,fill=Analysis)) +
  geom_col(position="dodge") +
  scale_fill_manual(values=c("#66CCCC","#006666")) +
  scale_x_continuous(breaks = drive.data$order,
                     labels = drive.data$Driver)+
  scale_y_continuous(limits=c(0,100),expand = c(0,0))+
  ylab("Percent")+xlab(NULL)+coord_flip() +
  guides(fill = guide_legend(reverse=T)) + theme_bw() +
  theme(legend.position = c(0.825,0.075),legend.title = element_blank())
```

@@

# Results
## Are structured decision making steps explicit in MSEs?
The majority of MSEs did not explicitly document how the stages of the MSE process -- defined using the SDM framework -- were completed (Table \@ref(tab:explicit)).  The most documented stage was the alternative stage, while 3 of the 30 studies explicitly documented a tradeoff analysis and 2 of the 30 documented a management decision.

@@

@@

<!-- ### What questions and management objectives do MSEs address? -->
<!-- Uncertainty in system parameters was the main driver of the system state, but a variety of drivers were considered across the random sample of MSEs (Figure \@ref(fig:driversPlot)). -->

<!-- ```{r driversPlot, fig.cap='Drivers included in MSE models', fig.height=6, out.width="100%"} -->
<!-- Driver.plot + -->
<!--   theme(text = element_text(size=14)) -->
<!-- ``` -->

<!-- More objectives were considered per MSE in the random sample than in the climate change MSEs (Table \@ref(tab:PerMSE)).  Climate change MSEs were less likely to consider economic and social objectives than the random sample (Table \@ref(tab:objectiveCategories)). -->

<!-- ```{r, PerMSE} -->
<!-- color_Pub <- which(per.MSE$Analysis=='Random Sample') -->
<!-- color_CC <- which(per.MSE$Analysis=='Climate Change') -->

<!-- per.MSE %>% -->
<!--   kable(align = "c", caption = "Number of objectives considered per management strategy evaluation") %>%   -->
<!--   row_spec(color_CC, color = "#66CCCC", background = "white") %>% -->
<!--   row_spec(color_Pub, color = "#006666", background = "white") -->
<!-- ``` -->

<!-- ```{r, objectiveCategories} -->
<!-- color_Pub <- which(objcat.data$Analysis=='Random Sample') -->
<!-- color_CC <- which(objcat.data$Analysis=='Climate Change') -->

<!-- objcat.data %>% -->
<!--   kable(align = "c", caption = "Objective categories considered in management strategy evaluations") %>% -->
<!--   row_spec(color_CC, color = "#66CCCC", background = "white") %>% -->
<!--   row_spec(color_Pub, color = "#006666", background = "white") -->
<!-- ``` -->

@@

# Introduction

**Lorem ipsum** dolor *sit amet*.

- Single asterisks italicize text *like this*. 
- Double asterisks embolden text **like this**.

Start a new paragraph with a blank line separating paragraphs.

- This will start an unordered list environment, and this will be the first item.
- This will be a second item.
- A third item.
    - Four spaces and a dash create a sublist and this item in it.
- The fourth item.

1. This starts a numerical list.
2. This is no. 2 in the numerical list.

# This Starts A New Section
## This is a Subsection
### This is a Subsubsection
#### This starts a Paragraph Block.

> This will create a block quote, if you want one.
Want a table? This will create one.

Table Header  | Second Header
------------- | -------------
Table Cell    | Cell 2
Cell 3        | Cell 4

Note that the separators *do not* have to be aligned.

@@

Almost forgot about creating a footnote.[^1] This will do it again.[^2]

[^1]: The first footnote
[^2]: The second footnote

Want to cite something?

>>>>

# Get map background for plotting the map
world <- borders("world", colour="gray50", fill="gray50", alpha=0.75) # create a layer of borders
```
text

```{r plots}
# Where MSEs have occured
map.data<-rbind(data_pub,data_CC) %>%
  select(map.col) %>%
  mutate(Drivers=str_extract(Drivers, "Climate Change")) %>%
  mutate(Drivers=replace_na(Drivers, "Random Sample"))

@@

Driver.plot<-ggplot(drive.data_pub,aes(x=order,y=Percent)) +
  geom_col() +
  scale_x_continuous(breaks = drive.data_pub$order,
                     labels = drive.data_pub$Driver)+
  scale_y_continuous(limits=c(0,100),expand = c(0,0))+
  ylab("Percent")+xlab(NULL)+coord_flip()+ theme_bw()
```

@@

# Results
## Are structured decision making steps explicit in MSEs?
The majority of MSEs did not explicitly document how the stages of the MSE process -- defined using the SDM framework -- were completed (Table \@ref(tab:explicit)).  The most documented stage was the alternative stage, while 3 of the 30 MSEs explicitly documented a tradeoff analysis and 2 of the 30 documented a management decision. One of the 30 documented either the roles of participants in the MSE process or that the results of the MSE were adopted.

@@

### What questions and management objectives do MSEs address?
Uncertainty in system parameters was the main driver of the system state, but a variety of drivers were considered across the random sample of MSEs (Figure \@ref(fig:driversPlot)).

```{r driversPlot}
drive.data_pub %>%
  mutate("Percent"=round(Percent,0)) %>% 
  select(Driver,Percent,Frequency) %>% 
  kable(align = "c", caption = "Prevalence of Explicit Documentation of stages in the MSE process")
```

More objectives were considered per MSE in the random sample than in the climate change MSEs (Table \@ref(tab:PerMSE)).  Climate change MSEs were less likely to consider economic and social objectives than the random sample (Table \@ref(tab:objectiveCategories)).

```{r, PerMSE}
color_Pub <- which(per.MSE$Analysis=='Random Sample')
color_CC <- which(per.MSE$Analysis=='Climate Change')

per.MSE %>%
  kable(align = "c", caption = "Number of objectives considered per management strategy evaluation") %>%
  row_spec(color_CC, color = "#66CCCC", background = "white") %>%
  row_spec(color_Pub, color = "#006666", background = "white")
```

```{r, objectiveCategories}
color_Pub <- which(objcat.data$Analysis=='Random Sample')
color_CC <- which(objcat.data$Analysis=='Climate Change')

objcat.data %>%
  kable(align = "c", caption = "Objective categories considered in management strategy evaluations") %>%
  row_spec(color_CC, color = "#66CCCC", background = "white") %>%
  row_spec(color_Pub, color = "#006666", background = "white")
```

@@

@@

@@
